---
title: "Yamazaru Menu: Exploring the Data of (My Favorite) Sushi"
author: "Victoria Pierce Crossland"
date: "2024-011-29"
output: html_document
---

#About Me + Addiditonal Context:
# I am a sushi lover that struggles to decide on what to order and happens to have skills in web-scraping, data-manipulatuion and analyisis. I definitey have some favorite sushi roll ingredients (love mango and jalapeño) as well as some I avoid (anything deep fried). If only I had an easy way to filter for my preferences without skimming over the menu over and over.. Oh wait.. Let's create it (then take it a step further.)

```{r, include=F}
if(!is.element('dplyr', installed.packages()[,1])){install.packages('tidyverse',dependencies = T)}
if(!is.element('gt', installed.packages()[,1])){install.packages('rvest',dependencies = T)}
if(!is.element('gtsummary', installed.packages()[,1])){install.packages('gt',dependencies = T)}
if(!is.element('forcats', installed.packages()[,1])){install.packages('forcats',dependencies = T)}
if(!is.element('ggplot2', installed.packages()[,1])){install.packages('ggplot2',dependencies = T)}
if(!is.element('rmdformats', installed.packages()[,1])){install.packages('rmdformats',dependencies = T)}

library(tidyverse)
library(rvest)
```
##Initial Data Scrape and Dataset Creation 
```{r}
#Load my favorite sushi menu
link <- "https://yamazarusouthend.com/charlotte-yamazaru-food-menu"
menu <- read_html(link)

#Grab HTML elements
menuitems <- menu %>% html_elements("h3") %>%
  html_text2()

descrip<- menu %>% html_elements(".food-item-description") %>%
  html_text()

menusection<- menu %>% html_elements("h2") %>%
  html_text()

price<- menu %>% html_elements(".food-price") %>%
  html_text()

#Combining and formatting
(vpmenu <- cbind(menuitems, descrip, price))

menusection2 <- c(rep("Appetizers", 33), 
                  rep("Salads", 10), 
                  rep("Ramen", 3), 
                  rep("Fried Rice", 5), 
                  rep("Soup", 3), 
                  rep("Rice Bowl", 5), 
                  rep("Side Items", 5), 
                  rep("Yakisoba", 4), 
                  rep("Sushi Rice Bowl", 4),
                  rep("Nigiri", 20),
                  rep("Classic Maki", 5),
                  rep("Moriawase", 6), 
                  rep("American Classic Roll", 11),
                  rep("Specialty Roll", 30),
                  rep("Dessert", 4))

cbind(menusection2, vpmenu)-> vpmenu

vpmenu <- as.data.frame(vpmenu) %>% 
  mutate(descrip= ifelse(descrip== "", menuitems, descrip),
         descrip= str_to_title(descrip))

#New Variable that Distinguishes by Protein
vpmenu %>% 
  mutate(Contains= case_when(
    (str_detect(descrip, "Crab|Tuna|Salmon|Sash|Octopus|Yellowtail|Calamari|Shima|Urchin|Tekka|Sake|Negi|Scorpion|Pcs|Squid|Eel|Ikura|Hamachi|Roe|Fish|Mackerel|Clam|Conch|Snapper|Shrimp|Scallops|Seafood")~ "Seafood"),
    str_detect(descrip, "Chicken")~ "Chicken",
    str_detect(descrip, "Beef")~ "Beef",
    str_detect(descrip, "Pork")~ "Pork",
    str_detect(descrip, "Tofu")~ "Tofu",
    str_detect(menuitems, "Roll")~ "Seafood",
    TRUE~ "Veggie")) %>% 
  mutate(Any_Raw_Items= case_when(
    (str_detect(menuitems, "[*]")~ "Contains Raw or Undercooked Items"),
    TRUE~ "Fully cooked items only"))->vpmenu

#Double Checking Items Assigned Veggie
print(unique(vpmenu %>%
      filter(Contains == "Veggie") %>%
      pull(menuitems)))


#Separating item description into ingredient columns
vpmenu %>% 
  separate(descrip, into= c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11"),
           sep=",|With|Over|And|/|[|]") -> vpmenu

#Pivoting longer for tidy df
vpmenu %>% 
  pivot_longer(!menusection2 & !menuitems & !price & !Contains & !Any_Raw_Items , 
               names_to= "IngredientNum", 
               values_to = "Ingredients") %>% 
  mutate(Ingredients= str_replace(Ingredients, "[.]", ""),
         Ingredients=str_replace(Ingredients, " *", ""),
         Ingredients= str_to_title(Ingredients),
         Ingredients= str_replace(Ingredients, "Dessing", "Dressing"),
         price= as.numeric(str_remove(price, "[$]")))->vpmenu


#Manually Fixing Typos
vpmenu %>% 
  mutate(Ingredients= case_when(
    menuitems == "Chef's Choice Sashimi*" & IngredientNum== "1" ~ "8 Pcs Sashimi*",
    menuitems == "Chef's Choice Sashimi*" & IngredientNum== "2" ~ "12 Pcs Sashimi*",
    menuitems == "Chef's Choice Sashimi*" & IngredientNum== "3" ~ "16 Pcs Sashimi*",
    menuitems == "Chef's Choice Sashimi*" & IngredientNum== "4" ~ "20 Pcs Sashimi*",
    menuitems == "Cream Cheese Dip" & IngredientNum== "1" ~ "Crab Sticks",
    menuitems == "Cream Cheese Dip" & IngredientNum== "2" ~ "Cream Cheese",
    menuitems == "Cream Cheese Dip" & IngredientNum== "3" ~ "Green Onion",
    menuitems == "Cream Cheese Dip" & IngredientNum== "4" ~ "Deep Fried Wanton Skin",
    TRUE ~ vpmenu$Ingredients)) %>% 
      mutate(price= case_when(
        menuitems == "Chef's Choice Sashimi*" & IngredientNum== "1" ~ 18.00,
        menuitems == "Chef's Choice Sashimi*" & IngredientNum== "2" ~ 22.00,
        menuitems == "Chef's Choice Sashimi*" & IngredientNum== "3" ~ 28.00,
        menuitems == "Chef's Choice Sashimi*" & IngredientNum== "4" ~ 35.00,
        menuitems == "Cream Cheese Dip" ~ 6.50,
        TRUE~ vpmenu$price))-> vpmenu

#Dropping NAs for Tidy DF
vpmenu %>% 
  drop_na(Ingredients)->vpmenutidy

vpmenutidy %>% 
  mutate(menuitems= str_replace_all(menuitems, "\\*", ""))->vpmenutidy


##Edits to match Uber Eats Dataset below
vpmenutidy %>% 
  mutate(menuitems= case_when(
    menuitems == "A"~ "A 5 Nigiri-Tuna Roll",
     menuitems == "B"~ "B 8 Nigiri-Shrimp Tempura Roll",
     menuitems == "C"~ "C 6 Nigiri-6 Sashimi & 1 Spider Roll",
      menuitems == "D"~ "D 12 Nigiri-Scorpion Roll",
       menuitems == "E"~ "E 10 Nigiri-Tuna Avocado Roll & Kiss Of Fire Roll",
       menuitems == "F"~ "F 8 Nigiri-8 Sashimi & 3 Kingdom Rolls",
        TRUE~ vpmenutidy$menuitems))->vpmenutidy
       

```

```{r}
library(writexl)
write_xlsx(vpmenutidy, "SushiMenu.xlsx")
```


# Uber Eats Ratings
## This is where things started to go wrong.. 
```{r}
library(tidyverse)
library(stringr)
library(rvest)

uber_eats_url= "https://www.ubereats.com/store/yamazaru/rYvdCPBHTB-n69iSWsmlHQ?diningMode=DELIVERY&ps=1&sc=SEARCH_SUGGESTION"

uber_eats <- read_html(uber_eats_url)

#Half of Data Coming Through
menu_uber_eats <- uber_eats %>% html_elements("li") %>%
  html_text()

#Maybe this Way? No
menu_uber_eats <- uber_eats %>%
  html_elements("span[data-testid='rich-text']") %>%
  html_text(trim = TRUE)
```



##Only part of the menu comes through with Rvest. This challenged me for what felt like forever and researching other packages to resolve the possible issue of Lazy Loading was unsuccessful. Moving onto next idea.
#Initally attempted to use Rselenium package 
#Try to download as PDF and scrape?
```{r}
library(pdftools)
library(pdftables)

yamazaru <- pdf_text("Yama_menu.pdf")

yamazaru <- as.data.frame(yamazaru)

#Wow - This is messy. Let's break it up.
yamazaru %>% 
  separate_rows(yamazaru, sep="                     ") %>% 
  drop_na() -> yama_sep

yama_sep[76:809,1]->trimmed_menu


trimmed_menu %>%
  separate(yamazaru, c("name", "split"), '•') %>% 
  separate(split, c("perc_liked", "num_votes"), '%')->trimmed_menu

subset <- trimmed_menu[3:734,] %>% 
  select(perc_liked, num_votes)

trimmed_menu[1:732,] %>% 
  select(name) %>% 
  cbind(subset) %>% 
  drop_na()->uber_eats_menu




uber_eats_menu %>% 
  mutate(name = str_to_title(trimws(name)),
         perc_liked = trimws(perc_liked),
         num_votes = trimws(num_votes),
         num_votes = str_replace_all(num_votes, "[^[:alnum:]]", ""))->uber_eats_menu

uber_eats_menu$num_votes <- as.numeric(uber_eats_menu$num_votes)
uber_eats_menu$perc_liked <- as.numeric(uber_eats_menu$perc_liked)



write_csv(uber_eats_menu, "uber_eats_menu.csv")
write_xlsx(uber_eats_menu, "uber_eats_menu.xlsx")
  
```




```{r}
menu_uber_eats <- read_csv("Downloads/menu_uber_eats.csv")

menu_uber_eats %>% 
  separate(`menu_uber_eats[4:26, ]`, c("columna", "columnb"), '•')->menu_uber_eats

menu_uber_eats %>% 
  mutate(columna = str_sub(menu_uber_eats$columna, end = -7))->menu_uber_eats
menu_uber_eats %>% 
  drop_na() -> menu_uber_eats

menu_uber_eats[18, 1]<- "Gladiator"
menu_uber_eats[19, 1]<- "Volcano"
menu_uber_eats[20, 1]<- "Kiss of Fire"

menu_uber_eats <- menu_uber_eats[-c(6), ] 

number_of_votes <- (str_extract_all(menu_uber_eats, "\\([^()]+\\)")[[2]])
number_of_votes <- as.data.frame(substring(number_of_votes, 2, nchar(number_of_votes)-1))

menu_uber_eats %>% 
  cbind(number_of_votes) -> menu_uber_eats


colnames(menu_uber_eats) <- c("menu_item", "remove_later", "num_votes")


menu_uber_eats$remove_later %>% 
  substr(1, 4) -> percent_ranked


percent_ranked<- as.data.frame(percent_ranked)

menu_uber_eats %>% 
  cbind(percent_ranked) -> menu_uber_eats

menu_uber_eats %>% 
  select(menu_item, num_votes, percent_ranked) -> menu_uber_eats

```



#Fuzzy Match Yamazaru and Uber Eats Yamazaru
```{r}
library(fuzzyjoin)
library(writexl)

#Joining Yamazaru Menu with Uber Eats Data
vpmenutidy %>% 
  stringdist_left_join(uber_eats_menu,
                       by = c(menuitems = "name"),
                       method= "jw",
                       max_dist= .2,
                       distance_col= "dist")%>%
  group_by(menuitems) %>%
  slice_min(order_by=dist, n=1) -> fuzzy_matched

stringdist_left_join

#Yamazaru has 145 unique items on their menu
length(unique(vpmenutidy$menuitems))
(unique(vpmenutidy$menuitems))

#Uber Eats only has 118 options
length(unique(uber_eats_menu$name))


fuzzy_matched %>% 
  rbind(vpmenutidy) %>% 
  distinct(menuitems, Ingredients, .keep_all = TRUE) -> joined_data


#Stringing all case when together
joined_data %>% 
  mutate(menuitems = 
           case_when(menusection2 %in% c("Yakisoba", "Soup", "Nigiri", "Fried Rice", "Ramen") ~ paste(menuitems, menusection2, sep= " "), 
                     menusection2 %in% c("Specialty Roll") ~ paste(menuitems, "Roll"),
                     TRUE ~ menuitems))-> almost_final

#Fixing some Typos
almost_final %>% 
  mutate(menuitems = case_when(menuitems == "Sambal Hand Roll Roll" ~ "Sambal Hand Roll",
        menuitems == "Negi Toro with Ikura Hand Roll Roll" ~ "Negi Toro with Ikura Hand Roll",
        menuitems == "Saru Hand Roll Roll" ~ "Saru Hand Roll",
         menuitems == "Grinch" ~ "Grinch Roll",
                     TRUE ~ menuitems)) %>% 
  select(menusection2:Ingredients, perc_liked, num_votes)->final_sushi_data

final_sushi_data[is.na(final_sushi_data)]<- 0

write_csv(final_sushi_data, "final_sushi_data.csv")
write_xlsx(uber_eats_menu, "final_sushi_data.xlsx")

```

# I now have create a tidy data set of Yamazaru's menu with rating info from Uber Eats. My next project: Let's throw this into a dashboard to create an interactive tool to choose your sushi rolls. 